### 2019-08-15 Writeup/Thesis/pages/design.tex
Changes; - More corrections made - Added a speed comparison graph

Due to the scarcity of attacks in a real-world setting users are often complacent about their occurrence. Therefore, in this experiment, attacks only occur 30\% of the time. This occurrence is a much higher value than in a real-world setting, but it is a balance between resources and realistic design. Alongside, this the first 5 trials of a new experiment is always benign. This inclusion is to ensure users are lulled into a level of complacency regarding the possibility of an attack.

@@

However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end. We believe, however, that attention will also play a part in defining the most important areas of comparison. The hypothesis is that the users attention will be lower in the middle sections of comparison where it peak at the start and end. All these aspects will require empirical evidence to arrive at a conclusion. Therefore, this consideration will need to be made when assessing the results of the experiment.

These attacks are ascending in complexity. The timeframe for finding a match was decided as 7-days with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid range GPU (AMD RX 480 was the example in experiments). Due to the long life time of PGP keys, 7 days was chosen as a reasonable length of attack, attackers can just leave the tool and have it compute potential keys for the target without any need for user engagement. This is also a maximum time, these attacks also include keys that have a shorter average computation time.

@@

Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions. More combinations makes the attack search quicker as there are more possibilities. Any key that exceeds this criteria is deemed as vulnerable is one of the three attack contexts. A list of these vulnerable keys are sampled from when an attack is simulated. The percentage of vulnerable keys will be explored in Chapter \ref{cha:Experiments}.

\subsubsection{Quality control}
\label{sec:exp2_quality}
As the previous experiment, participants will be sourced from MTurk. Therefore, again, quality control is and aspect that requires consideration. As with the previous study, initially screened native speakers will be used. The same process will be performed to recruit suitable workers. Two metrics will be used to detect invalid results. Audio button clicks and overall time taken.

Audio buttons clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked. If there are rounds without button clicks, this is a sign of non-attentiveness. The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task. This provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

Overall time taken is as the name suggest a recording of the time taken to complete the entire experiment. If users complete the experiment in an abnormally small amount of time it can be used as another detection for invalid responses. Anything below a certain threshold will be discarded.

\subsubsection{Considerations}
As with the previous experiment MTurk demographics will result in participants that are not reflective of the general population. Due to the attack context of this experiment is can be assumed that the youth of the participants will contribute to less successful attacks. Therefore, the results generated by this experiment can be loosely assumed as a best case scenario for the scheme. We predict a high attack success rate if assessed over the general population.

>>>>

Due to the scarcity of attacks in a real-world setting, users are often complacent about their occurrence. Therefore, in this experiment, attacks only occur 30\% of the time. This occurrence is a much higher value than in a real-world setting, but it is a balance between resources and realistic design. Alongside, this the first 5 trials of a new experiment is always benign. This inclusion is to ensure users are lulled into a level of complacency regarding the possibility of an attack.

@@

However, this may not be applicable in this context due to the user being linearly fed an audio stream that they cannot skip to the start or end. We believe, however, that attention also plays a part in defining the most important areas of comparison. The hypothesis is that the users' attention is lower in the middle sections of comparison, where it peaks at the start and end. All of these aspects require empirical evidence to conclude. Therefore, this requires consideration when assessing the results of the experiment.

These attacks are ascending in complexity. The timeframe for finding a match was decided as 7-days with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid-range GPU (AMD RX 480 was the example in experiments). Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack. The tool requires no user interaction once started, therefore, it can be left for an extended period to compute potential keys. This timeframe is also a maximum time, these attacks also include keys that have a shorter average computation time.

@@

Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions. More combinations make the attack search quicker. Any key that exceeds this criterion is deemed as vulnerable. A list of these vulnerable keys is sampled from when an attack is simulated. The percentage of vulnerable keys is explored in Chapter \ref{cha:Experiments}.

\subsubsection{Quality control}
\label{sec:exp2_quality}
Like the previous experiment, participants are sourced from MTurk. Therefore, again, quality control is an aspect that requires consideration. As with the previous study, initially screened native speakers are used, alongside the utilisation of the same process to recruit suitable workers. Two metrics are used to detect invalid results: audio-button-clicks and the overall-time.

Audio-buttons-clicks is the number of times the blue \textit{"Authenticate with partner over the phone"} button in Figure \ref{fig:expID} is clicked. If there are rounds without button clicks, this is a sign of non-attentiveness. The design choice was made to keep this as a result filter, as preventing non-clicks would be a trivial task. This design provides a way to detect and discard click-throughs\footnote{Workers that aim to complete the task as fast as possible, with no regard for the quality of responses}.

Overall-time is as the name suggest a recording of the time taken to complete the entire experiment. If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses. Anything below a certain threshold is discarded.

\subsubsection{Considerations}
As with the previous experiment, sampling from a  MTurk demographics results in a collection of participants that are not reflective of the general population. Due to the attack context of this experiment is can be assumed that the youth of the participants contributes to less successful attacks. Therefore, the results generated by this experiment can be loosely assumed as a best-case scenario for the scheme. We predict a high attack success rate if assessed over the general population.

### 2019-08-15 Writeup/Thesis/pages/evaluation.tex
Changes; - More corrections made - Added a speed comparison graph

\todo{Make this the last question to answer}

@@

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated. Further more the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for.

\todo{Give some tasty stats}

>>>>

@@

\section{Research Question \ref{goal:complexity}}
Research Question \ref{goal:complexity}: \textit{``What are the time and computation complexity required to generate a ’similar’ keys for a targeted key pair?''} has been discussed by the project, the actual generation of keys was shown in Section \ref{sec:key_gen} where actual keys were generated. Further more the distribution of key permutations on a set of real-world keys were discussed in Section \ref{sec:averagePerms} and \ref{sec:vulnKeys}. To achieve this the tool GreenOnion was developed where inspiration was gathered from a currently available tool known as Scallion. Experimentation results were gathered and displayed in Section \ref{sec:SvG} that showed the significant increase in the number of near-collision keys GreenOnion can test for with GreenOnion being able to handle in excess of 1.5 million keys. This is in comparison to maximum of 40 keys Scallion can compare.

### 2019-08-15 Writeup/Thesis/pages/experiments.tex
Changes; - More corrections made - Added a speed comparison graph

\section{Scallion vs GreenOnion}
\label{sec:SvG}
This section will compare Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.

Table \ref{tab:scallion_speed} shows the speed decline as the number of keys increase. Any number of keys over 45 resulted in a crash to the program.

\todo{Add screenshot of the exception}

\begin{table}[!h]
    \centering
    \begin{tabular}{|ll|}
        \hline
        \textbf{Scallion} & \\
        \hline
        OS & Windows 10 (May 2019) \\
        Version & Scallion-2.0\footnote{\url{https://github.com/lachesis/scallion/raw/binaries/scallion-v2.0.zip}} \\
        \hline
        \textbf{GreenOnion} & \\
        \hline
        OS & Linux Mint (Version: TODO) \\ 
        \hline
        \textbf{Hardware} & \\
        \hline
        GPU & GTX 750 Ti  \\
        CPU & AMD FX-6300 \\
        \hline
    \end{tabular}
    \caption{Testing environment}
\end{table}

\begin{table}[!h]
    \centering
    \begin{tabular}{|ll|}
        \hline
        \textbf{Number of keys} & \textbf{Speed} \\
        \hline
        1 & 1001.3 MH/s \\
        5 & 784.3 MH/s \\
        10 & 707.9 MH/s \\
        15 & 628.2 MH/s \\
        20 & 526.5 MH/s \\
        25 & 503.8 MH/s \\
        30 & 473.1 MH/s \\
        35 & 432.6 MH/s \\
        40 & 404.9 MH/s \\
        45+ & \textit{N/A} \\
        \hline
    \end{tabular}
    \caption{Scallion's speed decline}
    \label{tab:scallion_speed}
\end{table}
\todo{Plot scallion speed decline}

\todo{Show the maximum number of keys the tool can achive}

\section{Experiment 1 - Metric performance}
\todo{talk about participants like the second experiment with Stdev}

As discussed in Section \ref{exp:metric} the goal of the experiment was the cull the number of metrics to be assessed in the following experiment. This section will discuss the demographics of participants alongside the subsequent results.

\begin{table}[h!]
    \centering
    \begin{tabular}{|l|ll|}
        \hline
        Gender & Male: & 46.2\% \\
               & Female: & 53.8\% \\
        \hline
        Age:   & 18-24: & 10.6\% \\ 
               & 25-29: & 20.2\% \\ 
               & 30-39: & 30.8\% \\ 
               & 40-49: & 22.1\% \\ 
               & 50-59: & 11.5\% \\ 
               & 60-69: & 3.8\% \\ 
               & 70-79: & 1.0\% \\

        \hline
        Highest Education:  
        & GCSE:                 & 15.4\%  \\
        & A-Level/O-Level:      & 18.3\% \\
        & Bachelor's degree:    & 51.0\% \\
        & Master's degree:      & 13.5\% \\ 
        & PhD:                  & 1.9\% \\
        \hline

@@

\begin{table}[h!]
    \centering
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Metric} & \textbf{Average Rating}  & \textbf{$\sigma$}\\
        \hline
        Leven     & 3.66  & 1.15\\
        NYSIIS    & 2.92 & 1.31\\
        Metaphone & 2.56 & 1.32\\
        Phonetic Vec & 2.50 & 1.35\\
        Soundex & 2.08 & 1.12 \\
        \hline
        Random  & 1.16 & 0.46\\
        \hline
    \end{tabular}
    \caption{Average metric performance}
    \label{tab:exp1_results}
\end{table}

Table \ref{tab:exp1_demo} contains the demographical breakdown of the participants assessed. As it can be seen over 60\% of participants can be considered highly educated (Bachelor’s and up). This is not fully reflective of the general population and therefore, has to be considered when interpreting the results. All participants were sourced from the US, this again requires consideration due to the large range of dialects present that may bias the results. Further work could investigate the affect of location and dialect on similar results.

Overall, 104 participants were assessed in this study. Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having too low of a fluency rating. This was a necessary process to improve the health of the results.

Figure \ref{tab:exp1_results} shows the average results for the metrics. It can be seen that Levenshtein came out substantially above the rest. The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance. Levenshtein has a much larger proportion of 4 and 5 ratings than the alternatives. This performance may, however, be due to the visual way the comparisons are being performed. (Discussed in detail in Section \ref{sec:exp1_considerations}).

Due to the averages of Metaphone and Phonetic Vectors being so close standard deviation was used as the final decider. As it can be seen Megaphone has a slightly lower $\sigma$ value of that of Phonetic vectors, thus, contributing to the decision to select Metaphone to be carried over to the next experiment.

\subsection*{Considerations}
As discussed in Section \ref{sec:exp1_considerations} compromises were made in order to fullfil all requirement with a minimized cost. Levenshtein's abnormal performance further backs up concerns around the visual aspect biasing the performance of the metric. This will have to be considered when interpreting the results.

Even with the discussed issues, the aim of the experiment was to promptly reduce the number of metrics for use later in the project. This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. The results are also an improvement over informal ad-hoc methods. Further work could aim to reproduce this study with the proposed audio based design (See Section \ref{sec:exp1_considerations}).

@@

\section{Experiment 2 - Trustword attacks}
\label{sec:exp2}
The aim of this experiment is to quantify the success rate of the proposed attack. Design details for this experiment can be seen in Section \ref{sec:exp2_design}. This section will present and discuss the results of the experiment alongside a comparison to relevant literature.

@@

The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.41\%) to Female (49.59\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This makes this set of participants more educated than the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
\begin{table}[!h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Browser & Percentage \\
        \hline
        Chrome & 85.09\% \\
        Firefox & 12.20\% \\
        Safari & 1.90\% \\
        Other & 0.81\% \\
        \hline
    \end{tabular}
    \caption{Internet Browser breakdown}
    \label{tab:exp2_browser}
    \begin{tabular}{|l|l|}
        \hline
        Operating System & Percentage \\
        \hline

@@

As user-agent strings were collected for each participant collations of OS and internet browser versions was made possible. Tables \ref{tab:exp2_browser} and \ref{tab:exp2_os} contain the browser and OS breakdowns respectively. Chrome and Windows 10 seem to dominate the proportion of their respective domains alongside the surprisingly large proportion of workers utilizing older versions of Windows such as 7 or 8 (15.81\%).

\subsection*{Results}
Table \ref{tab:exp2_attacks} contains the break down of results for the experiment. It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%. The best performer when regarding attack strength, as expected is the 2 static words. Levenshtein's 2 static attack performed the best overall with a success rate of 32.05\%. The worst performer was Metaphone with an average of 16.88\% over its three levels of attacks. When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in exactly the same order.

@@

\subsection*{Considerations}
As previously mentioned, the set of recruited participants are more highly educated than the general population. This combined with the low average age contributes to an inevitable bias being introduced into the data. An assumption can be made that higher education leads to more skillful interaction with computer based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario. The attacks, therefore, would be expected to be more successful on less technical users. This, however, requires further research and possible empirical data to determine the validity of the assumption.

During this study the main task was to perform the authentication ceremony a large number of times. In the real-world the ceremony is a secondary task due to it not strictly being required. This alongside the potential for users to downplay the possibility of attack leads to the conclusion that the success rates could be much higher in a real-world setting. The assumption is that these results display the success rate for extremely attentive users where they will make sure to double check with their authentication partner multiple times. This is opposed to the assumption that the majority of users will aim to complete the task as quickly as possible.

\subsection*{Comparison to alternative literature}
This section will aim to compare the results of the experiment to similar literature.

Work by Kainda \textit{et al.}\cite{kainda2009usability} (previous discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment. They were the only study to use exactly 4 words, but differed on the size of dictionary (1024 words) and how a near-match was calculated. Near-matches were a difference in a single word but without the consideration for similarity, this is the unique aspect considered with this experiment.

However, with those aspect in mind attacks on words encoding received an overall success rating of 3.3\%, considerably lower than that of this study. In the worst case our simulated attacks achieved almost 3 times as many successes compared to this study.

Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. This is less similar to the experiment as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success for the PGP Word list was 8.78\%. As 10/14 words were kept static more comparable to the results of the highest attack strength ``2 static''. This leads to another 3 fold improvement in the success rates of our simulated attacks.

The final relevant paper to compare is that of Tan \textit{et al.}\cite{tan2017can}. This paper had the highest number of words assessed with 16 overall. With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}. The attack success was 14\% overall, this again compared to the highest attack assessed in the experiment results in a sizeable difference.

In conclusion, all similar literature had much lower attack success rates that the results presented in this experiment. With all papers using similarly designed words lists it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success. Alongside this, the consideration for similarity when calculating near-collisions could have also resulted in the higher attack success rates. This aspect is also a unique consideration compared to available literature.

>>>>

\section{Scallion vs GreenOnion}
\label{sec:SvG}

\begin{wraptable}[11]{r}{6cm}
    \centering
    \begin{tabular}{|ll|}
        \hline
        \textbf{Scallion} & \\
        \hline
        OS & Windows 10 (May 2019) \\
        Version & Scallion-2.0\footnote{\url{https://github.com/lachesis/scallion/raw/binaries/scallion-v2.0.zip}} \\
        \hline
        \textbf{GreenOnion} & \\
        \hline
        OS & Linux Mint (Version: TODO) \\ 
        \hline
        \textbf{Hardware} & \\
        \hline
        GPU & GTX 750 Ti  \\
        CPU & AMD FX-6300 \\
        \hline
    \end{tabular}
    \caption{Testing environment}
\end{wraptable}

\begin{figure}[h!]
    \centering
    \input{diagrams/graphs/speed.tex}
    \label{tab:scallion_speed}
    \caption{Speed comparison between Scallion and GreenOnion}
\end{figure}

This section compares Scallion and the newly designed GreenOnion ability to search for a large number of potential keys.

Figure \ref{tab:scallion_speed} shows the speed decline as the number of keys increases for Scallion. Any number of keys over 40 resulted in a crash for Scallion. GreenOnion's speed is almost perfectly consistent. It is slower up until  around 5 keys. This consistency is due to the overhead of the bloom filter; however, as the number of keys increase, the bloom filter's benefits become apparent. In this test, the bloom filter size was kept consistent at exactly 5,000 elements.

GreenOnion has been tested to handle more than 1.5 million keys with a slight reduction in performance. This improvement over Scallion is, therefore, substantial.

\section{Experiment 1 - Metric performance}

As discussed in Section \ref{exp:metric}, the goal of the experiment was the cull the number of metrics to be assessed in the following experiment. This section will discuss the demographics of participants alongside the subsequent results.

\begin{table}[h!]
    \centering
    \begin{tabular}{|l|ll|}
        \hline
        Gender & Male: & 44.44\% \\
               & Female: & 55.56\% \\
        \hline
        Age:   & 18-24: & 10.10\% \\
               & 25-29: & 20.20\% \\
               & 30-39: & 31.31\% \\
               & 40-49: & 21.21\% \\
               & 50-59: & 12.12\% \\
               & 60-69: & ~~4.04\% \\ 
               & 70-79: & ~~1.01\% \\

        \hline
        Highest Education:  
        & GCSE:                 & 13.13\% \\
        & A-Level/O-Level:      & 19.19\% \\
        & Bachelor's degree:    & 52.53\% \\
        & Master's degree:      & 13.13\% \\ 
        & PhD:                  & ~~2.02\%  \\
        \hline

@@

Overall, 104 participants were assessed in this study. Five results were discarded from the set due to either failing the attention questions (See in Section \ref{sec:exp1_qualitycontrol}) or having too low of a fluency rating. This dismissal was a necessary process to improve the health of the results.

Table \ref{tab:exp1_demo} contains the demographical breakdown of the reduced set of participants. The average ages of the participants were 37.3 years ($\sigma = 11.67$)with a split of 44.44\% of Males to 55.56\% of Females. As can be seen, over 60\% of participants can be considered highly educated (Bachelor’s and up). This level of education is not sufficiently reflective of the general population and therefore, has to be considered when interpreting the results. All participants were sourced from the US; this again requires consideration due to the broad range of dialects present that may bias the results. Further work could investigate the effect of location and dialect on similar results.

\begin{wraptable}[11]{r}{8cm}
    \centering
    \begin{tabular}{|l|l|l|}
        \hline
        \textbf{Metric} & \textbf{Average Rating}  & \textbf{$\sigma$}\\
        \hline
        Leven     & 3.66  & 1.15\\
        NYSIIS    & 2.92 & 1.31\\
        Metaphone & 2.56 & 1.32\\
        Phonetic Vec & 2.50 & 1.35\\
        Soundex & 2.08 & 1.12 \\
        \hline
        Random  & 1.16 & 0.46\\
        \hline
    \end{tabular}
    \caption{Average metric performance}
    \label{tab:exp1_results}
\end{wraptable}

Figure \ref{tab:exp1_results} shows the average results for the metrics. It can be seen that Levenshtein came out substantially above the rest. The breakdown of the ratings in Figure \ref{fig:exp1_breakdown} also shows Levenshtein's dominance. Levenshtein has a much more significant proportion of 4 and 5 ratings than the alternatives. This performance may, however, be due to the visual way the comparisons are being performed. (Discussed in detail in Section \ref{sec:exp1_considerations}).

Due to the averages of Metaphone and Phonetic Vectors being so close standard deviation was used as the final decider. As can be seen, Megaphone has a slightly lower $\sigma$ value of that of Phonetic vectors, thus, contributing to the decision to select Metaphone.

\subsection*{Considerations}
As discussed in Section \ref{sec:exp1_considerations}, compromises were made to fulfil all requirement with a minimized cost. Levenshtein's abnormal performance further backs up concerns around the visual aspect biasing the performance of the metric. This aspect requires consideration when interpreting the results.

Even with the discussed issues, the experiment was designed to reduce the number of metrics promptly. This experiment, therefore, has achieved that goal of providing three metrics for the subsequent experiment while balancing between accuracy and expenditure. The results are also an improvement over informal ad-hoc methods. Further work could aim to reproduce this study with the proposed audio-based design (See Section \ref{sec:exp1_considerations}).

@@

\section{Experiment 2 - Trustword attacks}
\label{sec:exp2}
This experiment aims to quantify the success rate of the proposed attack. Design details for this experiment can be seen in Section \ref{sec:exp2_design}. This section presents and discusses the results of the experiment alongside a comparison to relevant literature.

@@

The reduced set of 369 participants had an average age of 36.63 ($\sigma = 11.35$) and consisted of an almost equal split of Male (50.41\%) to Female (49.59\%). Around 62\% of participants had completed a single stage of university (Bachelor and up). This aspect makes this set of participants more educated than the general population. All participants were also sourced from the USA and have rated themselves as fully native English speakers.
\begin{table}[!h]
    \centering
    \begin{tabular}{|l|l|}
        \hline
        Browser & Percentage \\
        \hline
        Chrome & 85.09\% \\
        Firefox & 12.20\% \\
        Safari & 1.90\% \\
        Other & 0.81\% \\
        \hline
    \end{tabular}
    \caption{Internet Browser breakdown}
    \label{tab:exp2_browser}
    \begin{tabular}{|l|l|}
        \hline
        Operating System & Percentage \\
        \hline

@@

As user-agent strings were collected for each participant collations of OS and internet browser versions was made possible. Tables \ref{tab:exp2_browser} and \ref{tab:exp2_os} contain the browser and OS breakdowns,  respectively. Chrome and Windows 10 seem to dominate the proportion of their respective domains alongside the surprisingly large proportion of workers utilizing older versions of Windows such as 7 or 8 (15.81\%).

\subsection*{Results}
Table \ref{tab:exp2_attacks} contains the break down of results for the experiment. It can be seen that the best metric out of the set was Levenshtein with an overall success of 19.80\%. The best performer, when regarding attack strength, as expected, is the 2 static words. Levenshtein's 2 static attack performed the best overall with a success rate of 32.05\%. The worst performer was Metaphone, with an average of 16.88\% over its three levels of attacks. When comparing the performance of the metrics to the previous experiment the ordering remains the same with Levenshtein, NYSIIS and Metaphone all ranking in the same order.

@@

\subsection*{Considerations}
As previously mentioned, the set of recruited participants are more highly educated than the general population. This. combined with the lower average age, contributes to an inevitable bias being introduced into the data. An assumption can be made that higher education leads to more skilful interaction with computer-based systems, this, therefore, with the previous assumption in mind means the results of this experiment can be considered a `best case' scenario. The attacks, therefore, would be expected to be more successful on less technical users. This consideration, however, requires further research and possible empirical data to determine the validity of the assumption.

During this study, the main task was to perform the authentication ceremony a set number of times. In the real-world, the ceremony is a secondary task due to it not strictly being required. This aspect, alongside the potential for users to downplay the possibility of attack, leads to the conclusion that the success rates could be much higher in a real-world setting. The assumption is that these results display the success rate for extremely attentive users where they make sure to double-check with their authentication partner multiple times. It is, therefore, assumed that the majority of users aim to complete the task as quickly as possible, if at all.

\subsection*{Comparison to alternative literature}
This section compares the results of the experiment to similar literature.

Work by Kainda \textit{et al.}\cite{kainda2009usability} (previously discussed in Chapter \ref{cha:LiteratureReview}) is the most comparable to this experiment. They were the only study to use exactly 4 words but differed on the size of the dictionary (1024 words) and how a near-match were calculated. Near-matches were a difference in a single word, but without the consideration for similarity, this is the unique aspect considered with this experiment.

However, with those aspects in mind attacks on words encoding received an overall success rating of 3.3\%, considerably lower than that of this study. In the worst-case, our simulated attacks achieved almost 3 times as many successes compared to this study.

Other relevant work by Dechand \textit{el al.}\cite{dechand2016empirical} also discussed in Chapter \ref{cha:LiteratureReview} assess the success rate of attacks on words. Their experiment is less similar as 14 words per attack were assessed with each participant, where the comparison was performed visually. However, the success was 8.78\%. As 10/14 words were kept static, this result is more comparable to the highest attack strength ``2 static''. This, therefore, leads to another 3 fold improvement in the success rates of our simulated attacks.

The final relevant paper to compare is that of Tan \textit{et al.}\cite{tan2017can}. This paper had the highest number of words assessed with 16 overall. With it assessing the same wordlist and attack strength as the work by Dechand \textit{et al.}, the attack success was 14\% overall. This success rate compared to the highest attack assessed in the experiment results in another sizeable difference.

In conclusion, all related literature had much lower attack success rates that the results presented in this experiment. With all papers using similarly designed wordslists, it highly suggests that the deficiencies in Trustwords are the cause for the substantial increase in attack success. Alongside this, the consideration for similarity when calculating near-collisions could have also resulted in the higher attack success rates. This aspect is also a unique consideration compared to the available literature.
